TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems

### 2016-12-16 ISORC2017/diff/20161216.tex
Add 20161216.tex

TINET is a TCP/IP protocol stack for embedded systems.
TINET is a compact TCP/IP protocol stack, however consists of many complex source codes.
Therefore, it is difficult to maintain, extend, and analysis the software.

To improve the scalability and configurability, this paper has proposed a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
The component-based TINET provides software developers high productivity such as change of network buffer size and add/remove TCP (or UDP) function.
We evaluate the component-based TINET compared with the original TINET, and confirm that the overheads of execution time and memory consumption are low and  that the configurability is improved.

@@

TINET (Tomakomai InterNETworking) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
TINET needs small memory for its TCP/IP protocol stack, therefore it is suitable for embedded systems.
However, there are several issues that TINET consists of many complex source codes.
It may take a lot of time for software developers to maintain, extend, and analysis the software because TINET is composed of many files and defines many macros.

Component-based development is an approach to improve software productivity.
Component-based development is a design technique that can be applied to reusable software development \cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.
In addition, individual Component diagrams enable the visualization of an entire system.

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, that component behaviors and interconnections are defined statically, thus TECS can optimize the overhead of componentization.

@@

    \item {\bf Improve configurability}\mbox{}\\
        TINET+TECS is a component-based system, therefore the software is flexible to change the configuration such as resize network buffer, add/remove TCP (or UDP) functions, and support both IPv4 and IPv6.
        In addition, a component diagram provides visualization of TINET, a complicated system.

@@

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
To take restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:

@@

TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs due to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

@@

The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
A {\it signature} is the interface definition of a {\it cell}.
The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.

@@

In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
These components are described as follows.

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees,
               [in] uint32_t speed_abs,
                [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Fig.\ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

@@

\subsection{send, receive specifier}

TECS supports send and receive specifiers, which are interface specifiers \cite{par:RPC}.
TINET+TECS uses send and receive specifiers instead of in and out to reduce the number of copies.

in is a specifier for input arguments.
A callee side uses the memory of arguments with in while executing the callee function.
When the processing returns to the caller side, the caller can reuse and deallocate the memory.

send is also a specifier for transferring data to a callee from a caller such as in.
The difference between in and send is whether to deallocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
In case of in specifier, both allocating and deallocating the data memory are performed in the caller.
On the other hand, in case of send, the caller allocates the data memory and the callee deallocates it.

out is a specifier for output arguments.
A callee writes data in the memory allocated by a caller, and the caller receives the data.

receive is also a specifier for a caller receiving data from a callee such as out.
The difference between out and receive is whether to allocate the data memory in caller or callee, shown as Figure \ref{fig:SendReceive}.
While, in case of out, a callee writes data in the memory allocated by a caller, in case of receive, the callee allocates the data memory.
Deallocating the memory is performed in the caller in both cases.

@@

TECS supports {\it Adapter} functionality which enables to call a function in TECS from C codes.
An adapter connects a TECS component, links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.
Software developers can utilize an existing application for TECS owing to the adapter.

>>>>

TINET is a TCP/IP protocol stack for embedded systems.
Although TINET is a compact TCP/IP protocol stack, it consists of many complex source codes.
Therefore, it is difficult to maintain, extend, and analysis the software.

To improve the scalability and configurability, this paper has proposed a component-based TCP/IP protocol stack for embedded systems: TINET componentized with TOPPERS embedded component system (TECS).
The component-based TINET provides software developers high productivity such as change of network buffer size and adding/removing TCP (or UDP) function.
We evaluate the component-based TINET compared with the original TINET.
We confirm that the overheads of execution time and memory consumption are low, and that the configurability is improved.

@@

TINET (Tomakomai InterNETworking) is a compact TCP/IP protocol stack for embedded systems \cite{url:TINET}.
TINET supports the ability such as minimum copy frequency and elimination of dynamic memory control.
TINET needs only small memory for its TCP/IP protocol stack; therefore it is suitable for embedded systems.
However, there are several issues that TINET consists of many complex source codes.
In other words, TINET is composed of many files and defines many macros.
This may take a lot of time for software developers to maintain, extend, and analysis the software.

Component-based development is an approach to improve software productivity.
Component-based development is a design technique that can be applied to reusable software development \cite{par:CBD}, such as TECS \cite{par:TECS}, AUTOSAR \cite{url:AUTOSAR}, and SaveCCM \cite{par:SAVEapproach}.
Component-based systems are flexible to software extension and specification changes.
In addition, individual component diagrams enable the visualization of an entire system.

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.

@@

    \item {\bf Improve configurability}\mbox{}\\
        TINET+TECS is a component-based system, therefore the software is flexible to change the configuration such as resizing network buffer, adding/removing TCP (or UDP) functions, and support both IPv4 and IPv6.
        In addition, a component diagram provides visualization of TINET, a complicated system.

@@

TINET is a compact TCP/IP protocol stack for embedded systems based on the ITRON TCP/IP API Specification \cite{url:ITRON_TCP/IP_API_Spec}, developed by TOPPERS (Toyohashi OPen Platform for Embedded Real-time Systems) Project \cite{url:TOPPERS}.
To satisfy restrictions for embedded systems such as memory capacity, size, and power consumption, TINET supports following functions:

@@

TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs owing to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

@@

The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
A {\it signature} is the interface definition of a {\it cell}.
The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Note that {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.

@@

In TECS, components are described with component description language (CDL).
CDL can be divided into three categories: {\it signature}, {\it celltype}, and build description.
These components are described as follows.

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'', e.g., sMotor (Fig.\ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees,
               [in] uint32_t speed_abs,
                [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Fig.\ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Fig.\ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        A {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order to compose {\it cell}s,
        In Fig. \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

@@

\subsection{send/receive specifier}

TECS supports {\it send}/{\it receive} specifiers, which are interface specifiers \cite{par:RPC}.
TINET+TECS uses {\it send} and {\it receive} specifiers instead of {\it in} and {\it out} to reduce the number of copies.

{\it in} is a specifier for input arguments.
A callee side uses the memory of arguments with {\it in} during executing the callee function.
When the processing returns to the caller side, the caller can reuse and deallocate the memory.

{\it send} is also a specifier for transferring data to a callee from a caller such as {\it in}.
The difference between {\it in} and {\it send} is whether to deallocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
In case of {\it in} specifier, both allocating and deallocating the data memory are performed in the caller.
On the other hand, in case of {\it send}, the caller allocates the data memory and the callee deallocates it.

{\it out} is a specifier for output arguments.
A callee writes data in the memory allocated by a caller, and the caller receives the data.

{\it receive} is also a specifier for a caller receiving data from a callee such as {\it out}.
The difference between {\it out} and {\it receive} is whether to allocate the data memory in a caller or callee, shown as Fig. \ref{fig:SendReceive}.
While, in case of {\it out}, a callee writes data in the memory allocated by a caller, in case of {\it receive}, the callee allocates the data memory.
Deallocating the memory is performed in the caller in both cases.

@@

TECS supports {\it Adapter} functionality which enables to call a function in TECS from C codes.
An adapter connects a TECS component, and links a C function to a TECS function shown as Fig. \ref{fig:TECS_Adapter}.
Software developers can utilize an existing application for TECS owing to the adapter.
